---
output:
  github_document:
    html_preview: no
  html_document:
    df_print: paged
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

"binomial" is a package that provides functions to calculate the binomial probability distribution functions


* `bin_choose`  a function that computes the number of successes can occur in given trials
* `bin_probability`  a function that computes the probability of getting a particular number of successes in given trials.
* `bin_distribution`  a function that computes the probability distribution.
* `bin_cumulative` a function that computes the cumulative distribution.
* `bin_variable` creates a binomial random variable object (of class '"binvar"')
* `plot()` a method to display a histrogram of the `bin_distribution` and the cumulative probability of `bin_cumulative`
* `print()` a method to display a data frame of the object of class `binvar` 
* `summary()` a method to display all the measures of the object of class `binvar`
* `print.summary()` a method to display a data frame of the `summary()`


## Motivation

This package is to provide binomial probability distribution functions that illustrates binomial concepts. 


## Installation

Install the development version from GitHub via the package `"devtools"`:

```{r}


# development version from GitHub:
#install.packages("devtools") 
# install "binomial" (without vignettes)

devtools::install_github("anthony-repo/binomial/binomial")
# install "binomial" (with vignettes)
devtools::install_github("anthony-repo/binomial/binomial", build_vignettes = TRUE)


```


##Usage 

```{r}

library(binomial)
library(ggplot2)

# the number of combinations to choose 2 objects from 5 objects
bin_choose(n = 5, k = 2)

# the probability of getting 2 successes out of 5 trials
bin_probability(success = 2, trials = 5, prob = 0.5)

# probability distribution and its barplot
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
plot(dis1)

# probability distribution and the cumulative probability along with its graph
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
plot(dis2)

# creates a binomial random variable and displays its summary
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
binsum1 <- summary(bin1)
binsum1


```


